Chlorophylla

### 2019-02-28 Chlorophyll_a .Rmd
Update
fixed....maybe..

# Pixels and matching
match_index <- knnx.index(data = as.matrix(daily_chloro_data[,1:2]),
                          query = as.matrix(combined_US[,5:6]), k = 1)

# # # Select SST pixels nearest to insitu sites
pixel_match <- daily_chloro_data[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = combined_US$site)

>>>>

match_index <- knnx.index(data = as.matrix(MODIS_Chloro[,1:2]),
                          query = as.matrix(combined_US[,5:6]), k = 1)

pixel_match <- MODIS_Chloro[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = combined_US$site)
